\def\papersize{5}
\input{preamble.inc}

\begin{document}

\title{D-ESSU  -  BR23  -  Bristell B23-915 IFR}
\versionchecklist{EN-0.1.18}
\datechecklist{06/2025}

\begin{checklist}{Before Enginge Start}
  \item{Preflight Inspection  }{completed}
    \hint{According to Handbook, Cpt. 4.3}
  \item{Rudder Pedal Position}{set}
  \item{Seat belts}{tighten}
  \item{Flight Controls}{checked}
  \item{Canopy}{locked}
  \item{Parking Break}{set}
    \hint{Apply pressure and set, then 'pump'.}
  \decision{Use of ext. Power:}
    \step{See notes in Handbook Cpt. 4.4.2}
\end{checklist}

\begin{checklist}{Enginge Start}
  \item{Circuit Breakers}{checked}
  \item{Backup Battery}{on}
  \item{GTN650Xi, MFD, EFIS}{booting}
  \decision{MFD}
    \step{Wait for boot sequence.}
    \step{Check FUEL QTY!}
    \step{Conf. amber "BACKUP BATT" msg.}
    \step{Conf. CO vallue 255ppm, then decr.}

  \item{Master Switch}{ON}

  \decision{MFD}
    \step{Conf. amber "BACKUP BATT" msg.}
    \step{CAS message OFF}

  \item{Backup Battery}{off}
  \item{GEN A/B}{ON}
  \item{Voltage M }{Min. 12 V}
    \hint{(Batt/Alt-C Bus)}
  \item{Fuel Selector}{more empty tank}
  \item{Propeller Control}{fine}
    \hint{Fully forward}
  \item{Throttle}{closed}
  \item{Strobe Light}{ON}
  \item{LANE A / LANE B}{on}
  \item{Main Fuel Pump}{on} 

Continues next column!
\end{checklist}

\begin{checklist}{Continue: Enginge Start}
  \item{Start Power}{ON (hold!)}
  \decision{LANE A/B Lamps:} 
    \step{wait till lamps turn OFF}
  \item{MFD Engige Indication}{checked}
    \hint{-> active and correct}
    \hint{-> Fuel Pressure in Limits}
  \decision{Throttle Lever:}
    \step{Coolant/Oil \textcolor{blue}{Tmp. <10$^{\circ}$C} >= 55\%}
    \step{Coolant/Oil \textcolor{red}{Tmp. >10$^{\circ}$C} ca. 45\%}
    \hint{\% as indicated as "T" on MFD.}
    \hint{See HINT and Start Performance Chart }
    \hint{in Handbook Cpt. 4.4.3 on P. 4-8!}

  \decision{ENGINE START:}
    \hint{Hold "Start Power", THEN press "START"}
    \hint{until Eng. fires. Then release}
    \hint{Start-Button and "Start Power".}
  \item{Throttle: reduce to}{1700 - 2000~RPM}
  \item{Oil Pressure}{Checked}
  \item{LANE A / B}{Ind. Lamp OFF}
    \hint{Both switches remain ON!}
    \hint{The Indicator Lamps should go out.}
  \item{Throttle}{2500 RPM for 10 sec}
  \item{Voltage M / Voltage B}{13.4 / 14.0 V}
\end{checklist}

\begin{checklist}{After Engine Start}
  \item{Avionics}{ON}
  \item{ALT-C}{ON}
  \item{Voltage M}{checked}
    \hint{Increasing, nom. 13.8 V}
  \item{EFIS}{ON}
  \item{EFIS Power Source}{Checked}
    \hint{Verify NOT on internal Batt.}
  \item{Baro PFD + MFD}{set}
    \hint{StbyEFIS, GTN are synced. MFD isn't!}

  \decision{Engine Warm-Up:}
    \step{2500 RPM until oil temp > 50$^{\circ}$C.}
    \step{Then set throttle to IDLE.}
\end{checklist}

\begin{checklist}{Before Taxiing}
  \item{Nav Light (at night)}{as required}
  \item{Landing-/Taxi-Light}{as required}
    \hint{A/C moving: Lights on!}
  \item{PFD, stby EFIS, MFD}{checked}
    \hint{ADHRS stabilised.}
\end{checklist}

\begin{checklist}{Taxiing}
  \hint{Keep RPM < 2500, taxiing with}
  \hint{walking speed! Check breaks \& steering.}
  \item{Ground Control}{checked}
  \item{Brakes}{checked}
  \item{Indications}{checked}
    \hint{Attitude/direction: PFD, MFD, stby EFIS}
\end{checklist}

\begin{checklist}{Engine Run Up}
  \item{Parking Brake}{set}
  \item{Oil Temperature}{min 50$^{\circ}$C}
  \item{Propeller Control}{fine}
    \hint{fully forwaard}
  \item{Landing-/Taxi-Light}{as required}
    \hint{A/C standing still: Lights off!}

  \decision{Pump and Fuel Supply Check}
    \step{Throttle: 3000 RPM}
    \step{AUX Pump: ON, pressuere in limits}
    \step{AUX Pump Light: ON}
    \step{Main Fuel Pump: OFF}
    \step{Pressure still in limits: CHECKED}
    \step{Mail Fuel Pump: ON}

  \item{Fuel Tank}{Sides Switched}
  \item{Fuel Pressure}{Checked}
  \item{Fuel Tank}{fullest tank}

Continues next column!
\end{checklist}
\begin{checklist}{Continue: Engine Run Up}
  \decision{Wastegate/PVC/Lane}
    \step{Verify BRAKES are FULLY set!}
    \step{Throttle: FULL THROTTLE}
    \step{RPM: min 5700, max 5800}
    \step{Manifold Pressure: within LIMITS}
    \step{Manifold Temp: Below 65$^{\circ}$C}
    \step{Throttle: reduce to 4700 RPM}
    \step{LANE A:  OFF}
    \step{Max drop 250 RPM (aft. 15 sec.)}
    \step{Check ENG Params in Limits!}
    \step{LANE A:  ON (wait 3 sec.)}
    \step{LANE B:  OFF}
    \step{Max drop 250 RPM (aft. 15 sec.)}
    \step{Check ENG Params in Limits!}
    \step{LANE B:  ON (wait 3 sec.)}
  \item{Propeller Control}{checked}
    \hint{Cycle 3 times. Move lever SLOWLY}
    \hint{backwards, but fast forward.}
  \item{Throttle}{IDLE CHECK}
  \item{Trhottle}{Set 3000 RPM}
\end{checklist}

\begin{checklist}{Before Take-Off}
  \item{Instruments}{checked}
  \item{Pitot-heat}{as required}
  \item{Flight Controls}{checked}
  \item{Cockpit Canopy}{closed \& locked}
  \item{Seat Belts}{tightened}
  \item{AEPS System}{unlocked}
    \hint{store pin in middle compartment}
  \item{Engine Instruments}{checked}
  \item{Flaps}{FLAPS 1}

Continues next page!
\end{checklist}
\begin{checklist}{Continue: Before Take-Off}
  \decision{Autopilot}
    \step{Autopilot Switch: ON}
    \step{Engage, for each test}
    \step{Check if AP can be overpowered!}
    \step{Check AP Disconnect by:}
    \step{Any Trim input, AP-Disc. button.}
  \item{Trim}{T/O Position}
  \item{Autopilot Switch}{OFF}
  \item{Autopilot Panel LEDs}{ALL OFF}
\end{checklist}

\begin{checklist}{TAKE-OFF}
  \item{Landing-/Taxi-Light}{ON}
  \item{Brakes}{released}
  \item{Propeller Control}{full forward}
  \item{Throttle}{full power}
  \item{Airspeed Indication}{checked: alive}
  \decision{TAKE-OFF SPEEDS}
  \item{Nosewheel Unstick}{50 KIAS}
  \item{Lift-Off}{60 KIAS}
  \item{Initial Climb}{70 KIAS}
  \item{Flaps retract}{75 KIAS}
    \hint{Not less than 150 ft AGL}
  \item{Climb}{v$_{y}$78~KIAS} 
\end{checklist}

\begin{checklist}{Climb}
  \decision{Climbing Speeds}
    \step{v$_{y}$ best ROC 78~KIAS} 
    \step{v$_{x}$ best AOC 63~KIAS} 
  \item{Throttle}{Full Forward}
  \decision{Prop Control}
    \step{Set Engine Speed}
    \step{max. 5800 RPM for 5 min}
    \step{max continuous 5500 RPM}
  \item{instruments}{T \& P in limits}
  \item{AUX Pump}{off}
  \item{Fuel Pressure}{checked}
  \item{Landing Light}{As required}
\end{checklist}

\begin{checklist}{Cruise}
  \decision{Fuel Selector}
    \step{Switch every 25min, latest.}
    \step{Check for balanced quantity!}
    \step{See notes in AFM Cpt. 4.4.13.}
  \item{Throttle}{As required}
  \item{Prop Control}{max. 5500 RPM}
  \item{Fuel Flow}{Checked}
  \item{Pitot Heat}{As Required}

  \decision{Changes in PWR:}
  \item{\textcolor{red}{Increase~~Power $\Uparrow$}}{1. RPM - 2. MAP}
  \item{\textcolor{blue}{Decrease~Power $\Downarrow$}}{1. MAP - 2. RPM}
    
\end{checklist}

\begin{table}[!ht]
  \large
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  \cellcolor{black!90}\color{white}\textbf{PWR} & \cellcolor{black!90}\color{white}\textbf{RPM}  & \cellcolor{black!90}\color{white}\textbf{MAP} \\ \hline

  100~\% & 5500~RPM & 40.5~inHg \\ \hline
  75~\% & 5000~RPM & 33.0~inHg \\ \hline
  59~\% & 4500~RPM & 25.5~inHg \\ \hline

  \end{tabular}
\end{table}


\begin{checklist}{Decent}
  \item{Throttle}{15...17~inhg}
  \item{Prop Control}{Max 5000 RPM}
  \item{Airspeed}{90...100~KIAS}
  \item{Pitot-Heat}{As Required}
  \hint{Do NOT reduce to IDLE in}
  \hint{cold OAT environments!}
\end{checklist}

\begin{checklist}{Before Landing}
  \item{Seat Belt}{tightened}
  \item{Cockpit}{prepared}
  \item{Autopilot}{disengaged}
  \item{Autopilot Switch}{OFF}
  \item{Throttle}{as required}
  \item{Speed}{83~KIAS}
  \item{Flaps}{FLAPS 1}
  \item{Trim}{as required}
  \item{Landing Light}{ON}
  \item{AUX Pump}{ON}
  \decision{Final Approach}
  \item{Flaps}{FLAPS 2}
  \item{Speed}{65~KIAS}
  \item{Trim}{As Required}
  \item{Prop Control}{FINE (forward)}
  \item{Throttle}{SET}
    \step{Approx. 7~inHG,}
    \step{Maint. RPM > 2600}
\end{checklist}

\begin{checklist}{Balked Landing / Go-Around}
  \item{Throttle}{full forward}
  \item{Speed}{70~KIAS}
  \item{Flaps}{FLAPS 1}
  \item{Trim}{adjusted}
  \item{Climb}{v$_{y}$78~KIAS} 
    \hint{Follow T/O Procedures}
\end{checklist}

\begin{checklist}{Landing}
  \item{Throttle}{closed}
  \item{Touch-down}{MAIN WHEELS}
  \item{Brakes}{as needed}
  \item{Flaps}{retract}
\end{checklist}

\begin{checklist}{After Landing}
  \item{Flaps}{RETRACTED}
  \item{Engine Speed}{SET}
    \hint{Taxi with walking speed!}
  \item{Landing-/Taxi-Light}{ON}
  \item{Pitot Heat}{OFF}
  \item{AUX Fuel Pump}{OFF}
\end{checklist}

\begin{checklist}{Shutdown}
  \item{Parking Brake}{SET}
  \item{Landin-/Taxi-Light}{OFF}
  \item{Propeller Control}{FINE}
  \item{Engine Speed}{IDLE}
  \item{Instruments}{ALL IN LIMITS}
  \item{ALT-C}{OFf}
    \hint{Check Volts M >= 13.4~V!}
  \decision{min. 2min COOL-DOWN!}
    \step{Use timer in EFIS!}
  \item{Line A}{OFF}
  \item{after 2 sec, LAMP:}{checked on}
  \item{Line B}{OFF}
  \item{Main Fuel Pump}{Off}
  \item{Avionics}{OFF}
  \item{EFIS}{OFF}
  \item{GEN A/B}{OFF}
  \item{Master}{OFF}
  \item{AEPS Locking Pin}{inserted}
  \item{Parking Brake}{as required}
\end{checklist}

\begin{checklist}{Parking and tie-down}
  \item{LANE Switches Checked}{ALL OFF}
  \item{Master Switch Checked}{OFF}
  \item{Parking Brake}{SET}
    \step{For short time parking only,}
    \step{for long time, use chocks!}
  \item{Canopy}{closed \& locked}
  \decision{Aircraft SECURED}
\end{checklist}


\end{document}