\def\papersize{4}
\input{preamble.inc}

\begin{document}

\title{D-MMDY  -  PNR2  -  Pioneer 200}
\versionchecklist{EN-1.3.6}
\datechecklist{06/2025}

\begin{checklist}{Information}
 	\item{MTOM}{540\,kg}
  	\item{Useful Load (incl. Sprit)}{225\,kg}
  	\item{Max. Ammount of Fuel}{60\,${\ell}$ / 43\,kg}
    	  \hint{Useable Fuel 58\,${\ell}$ }
    	  \hint{SUPER unlead 95/98}
	\decision{Speeds:}
 	  \item{Never Exceed  -  v$_{NE}$ }{ 225\,km/h}
	  \item{Norm. Ops Speed  -  v$_{A}$}{166\,km/h}
	  \item{Max. Speed for Flaps.  -  v$_{FE}$}{140\,km/h}
	  \item{Best Glide  -  v$_{BG}$}{115\,km/h}
	  \item{Minimal Sink  -  v$_{ms}$}{95\,km/h}
\end{checklist}

\begin{checklist}{Cockpit}
	\item{Preflight Inspection}{performed}
	  \hint{Acc. to Handbook Capt. 4.1  (P.\,34)}
	\item{Fuel on Board}{checked}
	\item{Documents and Dipstick}{on board}
	\item{Seat Belts}{on}
	\item{Canopy}{locked}
\end{checklist}

\begin{checklist}{Before Enginge Start}
	\item{Parking Brake}{set}
	\item{Fuel Shutoff Valve}{open}
	\item{Avionic Switches}{ALL switches off}
	\item{Life-Saving Equipment (Chute)}{unlocked}
	  \hint{Put splint-pin in middle compartment,} 
	  \hint{and ignition key in the ignition-lock.}
	\item{Master Switch}{on}
	\item{Circuit breakers}{all in}
	\item{Flaps}{completely retracted (UP)}
\end{checklist}

\begin{checklist}{Enginge Start}
	\item{Strobes ("NAV LTS")}{ON}
	\item{Fuel Pump}{5\,SEC. on - then OFF}
	\item{Throttle}{idle}
	\item{Choke}{as required}
	  \step{\textcolor{blue}{Engine cold}: PULL+HOLD}
	  \step{\textcolor{red}{Engine warm}: no Choke, Throttle ca. \textbf{2\,mm}}
	\item{Prop Area}{clear}
	\item{Engine Start, via Key}{performed}
	\item{Enginge Rev, with Choke released}{max. 2000\,RPM}
	\item{Oil Pressure}{Green ARC}
	\decision{Avionic (Toggle Switches)}
	  \step{XPDR, Horizon, Master Radio:  3x ON}
	  \step{Transponder on device to STBY/GND}
	\item{Altimeter}{SET}
	  \hint{Analogue Altimeter AND G5}
	\item{Navigation Tablet}{AS REQUIRED}
\end{checklist}

\begin{checklist}{Taxi}
	\item{Headlights}{ON}
	\item{Engine Rev}{idle}
	  \hint{Release parking brake and brake manually.}
	  \hint{Perform brake check on first movement!}
	  \hint{Taxi always with walking pace and ONLY}
	  \hint{according to required clearances!}
\end{checklist}

\begin{checklist}{Before Take-Off}
	\item{Parking brake}{set}
	\item{Throttle}{idle}
	\item{Headlights}{off}
	  \hint{Warm-up enging with max. 2000\,RPM.}
	  \hint{until oil temp. min. 50$^{\circ}$C.}
	\item{Run-up Check}{performed}
	  \hint{At 3200\,RPM.   Max. drop 250\,RPM (L/R)}
	\item{Flight Controls (Stick)}{free}
	\item{Trim}{set}
	\item{Canopy}{double checked}
\end{checklist}

\begin{checklist}{Take-Off / Departure}
	\decision{For Line-Up:}
	  \item{Headlights}{ON}
	  \item{Transponder}{alt (Mode S, ADS-B)}
	  \item{Flaps}{as required}
	  \item{Fuel Pump}{ON}
	    \hint{Line-up only according to required clearances!}
	\decision{In Position / Take-Off}
	  \item{Throttle}{FULL FWD}
	    \hint{Rotation \textbf{earliest} at 65\,km/h.}
	    \hint{Best climb w/ FLAPS-1: 110\,km/m. Clean: 115\,km/h.}
	\item{Trim}{set}
	  \hint{At about 400 ft AGL, reduce Rev slightly.} 
	  \hint{Fuel Pumpe and lights OFF.}
	  \hint{Retract Flaps. Climb w/ 115 to 120\,km/h}
	  \hint{Adjust trim accordingly.}
\end{checklist}
	
\begin{checklist}{Cruise}
	\item{Flaps}{retracted}
	\item{Headlights}{OFF}
	\item{Fuel Pump}{Off} 
	 
	\decision{Powersetting:}
	  \step{Normal Cruise:     4750 to 5000\,RPM}
	  \step{Fast Cruise:    up to max. 5300\,RPM}
	    \hint{\textbf{CAUTION:} High fuel consumption from 5000\,RPM on!}
	\decision{Check engine instruments regularly}
\end{checklist}

\begin{checklist}{Approach}
	\item{Altimeter}{SET}
	  \hint{Analogue Altimeter AND G5}
	\item{Speed}{acc. Approach}
	\item{Altitude}{acc. Approach}
	\item{Headlights}{ON}
	\item{Flaps}{as required}
	  \hint{CHECK IND. AIR SPEED!}
	  \hint{Max. 140\,km/h for Flaps.}
	\item{Altitude}{Acc. Circuit or Clearance}
\end{checklist}

\begin{checklist}{Final Approach and Landing}
	\item{Fuel Pump}{on}
	\item{Flaps}{as required}
	\item{Final Approach w/o Flaps}{110\,km/h}
	\item{Final Approach w/ Flaps 1/2}{100\,km/h}
	\item{Touch-down}{90 - 95\,km/h}
\end{checklist}

\begin{checklist}{After Landing / Turn-Off}
	\item{Fuel Pump}{off}
	\item{Flaps}{fully retracted}
	\item{Transponder}{STBY or GND}
	\item{Trhottle}{idle}
	  \hint{Taxi according to clearances, clean}
	  \hint{and with walkin pace. If}
	  \hint{necessary on hand on brake lever}
\end{checklist}

\begin{checklist}{Shut-Down}
	\decision{At Parkingposition:}
	  \item{Throttle}{idle}
	  \item{Parking Brake}{set}
	  \item{Headlights}{off}
	  \item{XPDR, Radio, Horizon}{off}
	  \item{Trim}{neutral}
	  \item{Ignition (via key)}{off}
	  
	\decision{After Engine has STOPPED:}
	  \item{Strobes ("NAV LTS")}{off}
	  \item{Flaps}{fully extended}
	    \hint{Step-on protection! Check first, then:}
	  \item{MASTER}{off}
	  \item{Life-saving Eq. (Chute)}{secured}
	  \item{Ignition key}{removed}
	    \step{Put key into middle compartment.}
	  
	\decision{When getting out:}
	  \item{ALL Flip-Switches}{OFF!}
	  \item{Parking Brake}{as required}
	\decision{Will the A/C be moved?}
		\step{Parking Brake: released}
	\decision{Parking over night? Outside?}
		\step{Parking Brake: SET}
		\step{Controls: SECURED}
		\step{  | (Arrest stick w/ Harness!)}
		\step{Wheel Chocks?}
		\step{A/C tied down?}
		\step{A/C covered? (Tarpaulin) }
\end{checklist}

\end{document}
